---
title: "What is Westbrook's Outlook on the Lakers after LeBron's Return? Twitter Sentiment Analysis"
author: "Thuy-Nhi Nguyen"
date: "11/19/2021"
output: html_document
---

```{r}
# load in libraries

library("twitteR")
library("tm")
library("SnowballC")
library("wordcloud")
library("RColorBrewer")
library("syuzhet")
library("ggplot2")
library("rtweet")
library("tidytext")
library("dplyr")
library("graphics")
library("purrr")
library("stringr")
library("textclean")
```


```{r}
# authorize access to twitter api

api_key <- "moMqwahI89bouu0N4S2o39jg7"
api_secret <- "DShXkahhV3thrXirN1YWlkigPAQfqXqLaKhZpyAbfNkhGfzNOF"
access_token <- "1461864624395993097-zSiD41FRzeyO4Y17NfOvl5t3gUJATT"
access_token_secret <- "ysK99HYNkY9j3XQ982YeDuY6nnp3YXUzG4jsQ3nTBYaZV"
setup_twitter_oauth(api_key,api_secret,access_token,access_token_secret)
```
```{r}
# search twitter for tweets regarding Russell Westbrook
russ_tweet <- searchTwitter('russwest44', n = 500); head(russ_tweet)
```



```{r}
# search twitter for tweets regarding Lakers

lakers_tweet <- searchTwitter('Lakers', n = 500, lang = 'en'); head(lakers_tweet)
```


```{r}
# assign lakers tweets to a dataframe and create a csv file

tweetsdf <- twListToDF(lakers_tweet)
write.csv(tweetsdf, file='Lakers.csv')
# 11-19-2021 tweets 10PM
```

```{r}
# assign tweets regarding Russell Westbrook to a dataframe and create a csv file
tweetsdf1 <- twListToDF(russ_tweet)
write.csv(tweetsdf1, file='RussLakers.csv')
# 11-19-2021 tweets 10PM
```



```{r}
# create a corpus for lakers tweet dataframe
myCorpus <- Corpus(VectorSource(tweetsdf$text),
                   readerControl = list(reader=readPlain,
                                        language="en"))
```


```{r}
# create a corpus for tweets regarding Russell Westbrook

myCorpus1 <- Corpus(VectorSource(tweetsdf1$text),
                   readerControl = list(reader=readPlain,
                                        language="en"))
```

```{r}
# look at the lakers tweet data

inspect(myCorpus[1:10])
```
```{r}
# look at the Russell Westbrook related tweets

inspect(myCorpus1[1:10])
```

```{r}

myCorpus <- tm_map(myCorpus, removeWords, stopwords())
myCorpus <- tm_map(myCorpus, content_transformer(tolower))
myCorpus <- tm_map(myCorpus, content_transformer(removeNumbers))
myCorpus <- tm_map(myCorpus, stripWhitespace)
myCorpus <- tm_map(myCorpus, stemDocument)


remove_url <- function(x) gsub("http[^[:space:]]*","",x)
myCorpus <- tm_map(myCorpus,content_transformer(remove_url))

remove_at <- function(x) gsub("@\\w+", "", x)
myCorpus <- tm_map(myCorpus,content_transformer(remove_at))

remove_amp <- function(x) gsub("&amp", "", x)
myCorpus <- tm_map(myCorpus,content_transformer(remove_amp))

myCorpus <- tm_map(myCorpus, removeWords,c("amp", "ufef","laker","yoongi", "jin","joon", "find"))
```

```{r}
# clean up corpus regarding Russell Westbrook

myCorpus1 <- tm_map(myCorpus1, removeWords, stopwords())
myCorpus1 <- tm_map(myCorpus1, content_transformer(tolower))
myCorpus1 <- tm_map(myCorpus1, content_transformer(removeNumbers))
myCorpus1 <- tm_map(myCorpus1, stripWhitespace)
myCorpus1 <- tm_map(myCorpus1, stemDocument)


remove_url1 <- function(x) gsub("http[^[:space:]]*","",x)
myCorpus1 <- tm_map(myCorpus1,content_transformer(remove_url1))

remove_at1 <- function(x) gsub("@\\w+", "", x)
myCorpus1 <- tm_map(myCorpus1,content_transformer(remove_at1))

remove_amp1 <- function(x) gsub("&amp", "", x)
myCorpus1 <- tm_map(myCorpus1,content_transformer(remove_amp1))

myCorpus1 <- tm_map(myCorpus1, removeWords,c("amp", "ufef"))
```

```{r}
myCorpus
```
```{r}
myCorpus1
dtm <- DocumentTermMatrix((myCorpus1))
```


```{r}
dtm <- DocumentTermMatrix((myCorpus))
```









```{r}
# start of sentiment analysis of lakers tweets
emotions <- get_nrc_sentiment(myCorpus$content)
```

```{r}
# start of sentiment analysis of Russell Westbrook related tweets
emotions1 <- get_nrc_sentiment(myCorpus1$content)
```


```{r}
# find count of 8 emotional sentiments of lakers tweets

barplot(colSums(emotions),cex.names = .7,
        col = rainbow(10),
        main = "Sentiment scores for Lakers tweets"
        )
```
$\textbf{Figure 1: Bar Plot showing the count of words in the Lakers tweets, associated with each emotion}$


```{r}
# find count of 8 emotional sentiments of Russell Westbrook tweets

barplot(colSums(emotions1),cex.names = .7,
        col = rainbow(10),
        main = "Sentiment scores for tweets related to Russell Westbrook"
        )
```

$\textbf{Figure 2: Bar Plot showing the count of words in the tweets related to Russell Westbrook, associated with each emotion}$





```{r}
# create word cloud of commonly words used in Lakers tweets

wordcloud(myCorpus, min.freq = 5)
```
$\textbf{Figure 3: Word cloud showing the commonly used tweet words regarding Lakers}$


```{r}
# create word cloud of commonly used words in Russell Westbrook related tweets

wordcloud(myCorpus1, min.freq = 5)
```
$\textbf{Figure 4: Word cloud showing the commonly used tweet words regarding Russell Westbrook}$

